\vskip-0.6in Trade Agreements in the Shadow of Lobbying\protect\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}

### 2016-01-22 draft.tex
compile draft for first time, fix footnote on title

\begin{document}
\title{\vskip-0.6in Trade Agreements in the Shadow of Lobbying\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}}
\thanksmarkseries{alph}
\author{Kristy Buzard\thanks{Syracuse University, Economics Department, 110 Eggers Hall, Syracuse, NY 13244, USA. Ph: 315-443-4079. Fax: 315-443-3717. Email: kbuzard@syr.edu. http://faculty.maxwell.syr.edu/kbuzard.}} 
\date{\vskip-.1in \today}
\maketitle

>>>>

\begin{document}
\title{\vskip-0.6in Trade Agreements in the Shadow of Lobbying\protect\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}}
\thanksmarkseries{alph}
\author{Kristy Buzard\thanks{Syracuse University, Economics Department, 110 Eggers Hall, Syracuse, NY 13244, USA. Ph: 315-443-4079. Fax: 315-443-3717. Email: kbuzard@syr.edu. http://faculty.maxwell.syr.edu/kbuzard.}} 
\date{\vskip-.1in \today}
\maketitle
